Append_smoothed_results

### 2016-11-24 Code/append_smoothed_results.Rmd

  if(length(white.index) != 0 & length(black.index) != 0) {
    list.age.decomp.tables.smoothed[[i]] <- le_age_decomp(life.table1 = as.data.frame(list.life.tables.smoothed[[black.index]]),
                                                          name.lt1 = "Black", 
                                                          life.table2 = as.data.frame(list.life.tables.smoothed[[white.index]]),
                                                          name.lt2 = "White", age.groups = "Age3")
  } else {
    list.age.decomp.tables.smoothed[[i]] <-"Couldn't compare life tables"
  }
  print(i)
}
```

@@

  if(length(white.index) != 0 & length(black.index) != 0) {
    ct.white <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexWhite"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_smoothed_deaths) %>%
                rename(prop.white = cod_prop_smoothed_deaths)

    ct.black <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexBlack"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_smoothed_deaths) %>%
                rename(prop.black = cod_prop_smoothed_deaths)
    ct.both <- merge(ct.white, ct.black, by = c("Age2", "COD2")) 
    ct.both <- ct.both %>% arrange(COD2, Age2)

@@

for(i in 1:dim(paired.ids)[1]) {
    if(list.cod.decomp.tables.smoothed[[i]][1] != "Couldn't compare life tables" & 
       list.cod.decomp.tables.smoothed[[i]][1] != "Encountered age group with no deaths") {

       list.cod.marginal.tables.smoothed[[i]] <- list.cod.decomp.tables.smoothed[[i]] %>% 
                                                  group_by(Cause.of.death) %>% 
                                                  summarise(C_x_COD = sum(C_xi))

@@

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, BlackWhiteSmooth, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     list.age.decomp.tables5, list.cod.decomp.tables5, list.age.decomp.tables9, list.cod.decomp.tables9,
     list.age.decomp.tables.smoothed, list.cod.decomp.tables.smoothed, list.cod.marginal.tables.smoothed,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

  if(length(white.index) != 0 & length(black.index) != 0) {
    list.age.decomp.tables.smoothed[[i]] <- le_age_decomp(life.table1 = as.data.frame(list.life.tables.smoothed[[black.index]]),
                                                          name.lt1 = "Black", 
                                                          life.table2 = as.data.frame(list.life.tables.smoothed[[white.index]]),
                                                          name.lt2 = "White", age.groups = "Age2")
  } else {
    list.age.decomp.tables.smoothed[[i]] <-"Couldn't compare life tables"
  }
  print(i)
}
```

@@

  if(length(white.index) != 0 & length(black.index) != 0) {
    ct.white <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexWhite"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_smoothed_deaths) %>%
                dplyr::rename(prop.white = cod_prop_smoothed_deaths)

    ct.black <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexBlack"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_smoothed_deaths) %>%
                dplyr::rename(prop.black = cod_prop_smoothed_deaths)
    ct.both <- merge(ct.white, ct.black, by = c("Age2", "COD2")) 
    ct.both <- ct.both %>% arrange(COD2, Age2)

@@

for(i in 1:dim(paired.ids)[1]) {
    if(list.cod.decomp.tables.smoothed[[i]][1] != "Couldn't compare life tables" & 
       list.cod.decomp.tables.smoothed[[i]][1] != "Encountered age group with no deaths") { 
       list.cod.marginal.tables.smoothed[[i]] <-  list.cod.decomp.tables.smoothed[[i]] %>%
                                                  dplyr::group_by(Cause.of.death) %>% 
                                                  dplyr::summarise(C_x_COD = sum(C_xi)) %>%
                                                  dplyr::mutate(C_x_COD_proportion = C_x_COD/sum(C_x_COD),
                                                         adds_to_gap = ifelse(C_x_COD > 0, T, F))

@@

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, BlackWhiteSmooth, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     list.age.decomp.tables5, list.cod.decomp.tables5, list.age.decomp.tables9, list.cod.decomp.tables9,
     list.age.decomp.tables.smoothed, list.cod.decomp.tables.smoothed, list.cod.marginal.tables.smoothed,
     non.zero.stratums, non.zero.stratums.smoothed,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```
